A dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-02-07 JTB_ms/JTB_ms.Rmd
add Fig. 2 legend

![Alternate stable states](../img/Fig2.png)

>>>>

![Alternate stable states in S:H biomass and growth across a light gradient. Alternate stable states occur between ~33-44 mol photons m^-2^ d^-1^ under these conditions (DIN=1e-7 molN L^-1^; X=2e-6 molX L^-1^), depending on whether initial S:H is high (0.1, closed circles), representing a healthy coral, or low (0.0001, open circles), representing a bleached coral.](../img/Fig2.png)
